Oral anticoagulants

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
adding warfarin proportion analyses

```{r prep-data}
## Drugs of interest
oral_anticoagulants <- 
  c("0208020H0", "0208020Z0", "0208020X0", "0208020AA", "0208020W0", 
    "020802000", "0208020I0", "0208020N0", "0208020S0", "0208020Y0", 
    "0208020V0")

@@

## Sort into monthly count data
oac_monthly_count <- oac %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

@@

```{r}
system.time(oac_gp_fcsts <-
              oac_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts())
oac_gp_fcsts %>%
  write_rds("../data/oac_gp_fcsts_1.rds")

oac_gp_cluster_fcsts <- 
  read_rds("../data/oac_gp_fcsts_1.rds")
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

>>>>

```{r prep-data}
## Drugs of interest
oral_anticoagulants <- 
  c("0208020H0", "0208020Z0", "0208020X0", "0208020AA", "0208020W0", 
    "020802000", "0208020I0", "0208020N0", "0208020S0", "0208020Y0", 
    "0208020V0")
warf <- "0208020V0"

@@

## Sort into monthly count data
oac_monthly_count <- oac %>% 
  group_by(datename, bnfchem) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = n / sum(n)) %>% 
  filter(bnfchem == warf) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>%
    as_tsibble(index = datename)
```

```{r prep-data}
  propRegional <- function(data, region, datename = datename, unit = Quantity){
  # Function to create tsibble object for a proportion of a drug by a given `unit` 
  # per `datename`
  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
  # the number of days in each month.
  region <- enquo(region)
  datename <- enquo(datename)
  unit <- enquo(unit)

  data %>%
    mutate(regional_unit = as_factor(set_names(!!region))) %>%
    group_by(regional_unit, !!datename) %>%
    summarise(n = sum(!!unit)) %>%
    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
                         str_detect(!!datename, pattern = "-03-") ~ n/31,
                         str_detect(!!datename, pattern = "-04-") ~ n/30,
                         str_detect(!!datename, pattern = "-05-") ~ n/31,
                         str_detect(!!datename, pattern = "-06-") ~ n/30,
                         str_detect(!!datename, pattern = "-07-") ~ n/31,
                         str_detect(!!datename, pattern = "-08-") ~ n/31,
                         str_detect(!!datename, pattern = "-09-") ~ n/30,
                         str_detect(!!datename, pattern = "-10-") ~ n/31,
                         str_detect(!!datename, pattern = "-11-") ~ n/30,
                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
    ungroup() %>%
    as_tsibble(index = !!datename, key = regional_unit)
}

@@

```{r}
regionalJointFcsts <- function (data, h = "5 months", keep_fits = FALSE) 
{
  if (!is.logical(keep_fits)) {
    stop("`keep_fits` must be of type logical")
  }
  regions <- unique(data$regional_unit)

  cl <- parallel::makeCluster(8)
  plan(cluster, workers = cl)

  fable_fcst <- 
    future_map_dfr(.x = regions, 
                   .f = ~fableModels(filter(data, 
                                            regional_unit == .x)) %>% 
                     forecast(h = h) %>% as_tibble(), 
                   .options = furrr_options(seed = TRUE))

  message("fable fits complete, step 1/4")
  message("fable forecasts complete, step 2/4")

  prophet_fcst <- 
    future_map_dfr(.x = regions, 
                   .f = ~prophetModels(filter(data, 
                                            regional_unit == .x)) %>% 
                     forecast(h = h) %>% as_tibble(), 
                   .options = furrr_options(seed = TRUE))
  message("prophet fits complete, step 3/4")
  message("prophet forecasts complete, step 4/4")

  parallel::stopCluster(cl)
  plan(sequential)
  joint_fcst <- dplyr::bind_rows(fable_fcst, prophet_fcst) %>% 
    dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 
      0.1), med = median(n), ub_80 = quantile(n, 0.9), 
      ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
      dist = n, n = NULL)
      return(list(forecasts = joint_fcst))
}

system.time(oac_gp_fcsts <-
              oac_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts(keep_fits = TRUE))

oac_gp_fcsts %>%
  write_rds("../data/oac_gp_fcsts_2.rds")

oac_gp_cluster_fcsts <- 
  read_rds("../data/oac_gp_fcsts_2.rds")
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```
